Escaping RGBland: Selecting Colors for Statistical Graphics

### 2013-01-23 pkg/colorspace/paper/Palettes/AuthorsResponse.tex
moved the colorspace package into its own subdirectory
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@94 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

        Yes, uniformity is a bit more complicated. Hence, we refrain from 
	discussing its details explicitly here, and have included some
	remarks in Section~3 pointing out that the CIELUV model also has
	limitations.

@@

	We have included pointers to Kaiser and Boynton (1996) and Knoblauch (2002)
	at the beginning of Section~3, and also included some further references
	to the computer graphics literature in other sections. We have kept the
	Wikipedia references because we agree with the referee that they are
	helpful (especially as a first overview).
\end{itemize}

@@

\begin{itemize}
  \item \textit{This is a potentially useful paper, although right now it needs more
        work.  The paper is lacking several common statistics examples: a
        scatterplot, barchart or mosaic plot, to introduce and establish the
        credentials of the color choices. Cindy Brewer's work covers maps very
        nicely. But the big problem in using these methods for statistical
        graphics is that we don't have large swatches of adjoining colour.}\\[-0.3cm]

@@

	This is a good point! All functions have been moved from vcd to colorspace,
	as of vcd~1.2-0 and colorspace~0.97.

>>>>

        Yes, uniformity is a bit more complicated. Hence, we refrain from 
	discussing its details explicitly here, and have instead included several
	remarks in Sections~1 and 3 conveying some limitations of the CIELUV model.

@@

	We have included additional pointers to Kaiser and Boynton (1996) and Knoblauch (2002)
	at the beginning of Section~3, and also included some further references
	to the computer graphics literature in other sections. We have kept the
	Wikipedia references because we agree with the referee that they are
	helpful (especially as a first overview).
\end{itemize}

@@

\begin{itemize}
  \item \textit{This is a potentially useful paper, although right now it needs more
        work.  The paper is lacking several common statistics examples: a
        scatterplot, barchart or mosaic plot, to introduce and establish the
        credentials of the color choices.}\\[-0.3cm]

@@

	This is a good idea! All functions have been moved from vcd to colorspace,
	as of vcd~1.2-0 and colorspace~0.97.
